% LaTeX Curriculum Vitae Template
%\
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/

% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{eurosym}
\usepackage{romannum}
% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Guohui Jiang}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, guohui, jiang},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers and footers
\usepackage{fancyhdr, lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0 pt}
\cfoot{\thepage\ of \pageref*{LastPage}}
\fancypagestyle{firstpage}
{
	\renewcommand{\headrulewidth}{0 pt}
    \fancyhead[L]{}    
    \fancyhead[R]{Last updated: \today}
}
\thispagestyle{firstpage}
%If it appears on every page
%\pagestyle{fancy}
%\renewcommand{\headrulewidth}{0 pt}
%\rfoot{Last updated: \today} 

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}
\pagenumbering{arabic}

% Place name at left
{\huge \name}
% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  University of Zurich \\
  \href{https://www.econ.uzh.ch/en.html}{Department of Economics} \\
  Schönberggasse 1 \\
  8001 Zurich, Switzerland
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & +41 44 634 55 73 \\
    Email: & \href{mailto:guohui.jiang@econ.uzh.ch}{guohui.jiang@econ.uzh.ch} \\
    Homepage: & \href{https://gjiang-economics.github.io}{https://gjiang-economics.github.io} \\
    Gender: & Male
  \end{tabular}
\end{minipage}

\section*{\MakeUppercase{Research Fields}}
\begin{itemize}
	\item Economic History, Political Economy, Cultural Economics, and Economic Growth
\end{itemize}

\section*{\MakeUppercase{education}}
\begin{itemize}
  \item PhD in Economics, University of Zurich, 2019-
  %\begin{itemize}
  %    \item PhD Dissertation:
  %\end{itemize}
  \item MSc in Economic Theory and Econometrics, Toulouse School of Economics, 2019.
  %\item BSc in Economics, Shandong University, 2017.

\end{itemize}

\section*{\MakeUppercase{work in progress}}
\begin{itemize}
	\item ``Discrimination and Talent Allocation: Evidence from Tuskegee Airmen'', with \href{http://www.jvoth.com}{Hans-Joachim Voth}.
\end{itemize}

\section*{HONORS $\&$ AWARDS}
\begin{itemize}
    \item \href{https://www.research.uzh.ch/en/funding/phd/uzh-doc-mobility.html}{UZH Doc.Mobility Fellowship}, CHF $51,373$, 2023.
    \item \href{https://www.ubscenter.uzh.ch/en/scholarships.html}{UBS Scholarship}, CHF $42,500$ per annum, 2019-2024.
    \item Bourse d'Excellence, Université Toulouse 1 Capitole, \euro $1,500$, 2019.
    \item L’Association Jean-Jacques Laffont Scholarship, \euro $6,000$, 2018.
\end{itemize}

\section*{\MakeUppercase{academic activities}}
\subsection*{Referee}
\begin{itemize}
    \item \textit{Economic Journal}. % 1
\end{itemize}
\subsection*{Summer Schools}
\begin{itemize}
    \item ASREC Graduate Student Workshop (Virtual), Chapman University, April 2022.
\end{itemize}
\subsection*{Services}
\begin{itemize}
    \item Co-organizer, Reading Group in Cultural Economics and Political Economy, University of Zurich, 2021-
    \item Member, Culture and Diversity Committee, Department of Economics, University of Zurich, 2021-2022.
\end{itemize}

%\section*{\MakeUppercase{employment}}
%\begin{itemize}
%    \item Research Assistant for \href{https://www.fbe.hku.hk/people/zhiwu-chen}{Zhiwu Chen} and \href{https://chichengma.weebly.com}{Chicheng Ma}, University of Hong Kong, 2019.
%\end{itemize}

\section*{\MakeUppercase{teaching}}
\subsection*{University of Zurich}
\begin{itemize}
	\item Research Frontiers in Economic History (MA), Instructor: 2022 Fall.
    \item Pioneering Economics (BA), TA for \href{https://www.econ.uzh.ch/en/people/faculty/hemous.html}{David Hémous}: 2022 Spring.
    \item Advanced Microeconomics I (MA), TA for \href{https://www.econ.uzh.ch/en/people/faculty/weber.html}{Roberto Weber}: 2021 Fall.
    \item Auction Theory (BA), TA for \href{https://www.econ.uzh.ch/en/people/faculty/ewerhart.html}{Christian Ewerhart}: 2021 Spring.
\end{itemize}
\subsection*{Toulouse School of Economics}
\begin{itemize}
    \item Macroeconomics \Romannum{2} (BA), TA for \href{https://www.tse-fr.eu/people/sumudu-kankanamge}{Sumudu Kankanamge}: 2019 Spring.
\end{itemize}

\section*{\MakeUppercase{Others}}
\begin{itemize}
    \item Languages: Chinese, English.
    \item Software: Stata, R, Python, QGIS, \LaTeX.
    \item Citizenship: China.
\end{itemize}
\bigskip

% Footer
%\begin{center}
%  \begin{footnotesize}
%    Last updated: \today
%  \end{footnotesize}
%\end{center}

\end{document}
